Use Of Jigsaw Puzzle Solving Algorithms In The Real World

### 2023-06-05 LaTeX_paper/paper.tex
finish section 3.3 (GA)

>>>>

This paper applies a genetic algorithm to the jigsaw puzzle problem, with some promising results.\newline
The algorithm seems to have a \(O(N^2)\) time complexity, with time slightly lower than the previous example
(But it is impossible to know for sure which one is faster, given that they didn't specify the hardware used).\newline
The paper has used the same method to evaluate accuracy that the previous one used
(neighbors comparison) so it is easy to compare them.\newline
The algorithm falls in the “Non binary comparison”~\ref{document:comparator};
this should give it an advantage, since it has more data to work with.\newline
Unfortunately this advantage does not compensate for the worst precision
of the algorithm itself, and the accuracy results are equivalent,
if not slightly worse than the previous algorithm.\newline
It is important to keep in mind that for the very nature of genetic algorithms,
it might be possible that the accuracy would have been better if they had allowed
it to run for more generations.\newline
Is also important to note that the discussed algorithm works with digital puzzles,
and this gives it the advantage of having more precise data.\newline
Whether this algorithm could work with a real world puzzle will be discussed
in section DOTO INSERT RFERENCE.
